---
title: "Rendering Parameterized RMarkdown Reports"
author: "MAJ Jim Pleuss, USMA"
date: "October 23, 2019"
output: 
  ioslides_presentation:
    incremental: true
    widescreen: true
---

#Context of the Problem

##Course End Feedback at West Point 

- In AY19-2 West Point transitioned to a new Course End Feedback system with inadequate functionality.  

- Goal: Create a unique summarized report for every department, program, and course at West Point with graphical depictions of course end feedback for every question in AY19-2.

- Added Bonus: Provide comparisons of responses to the same questions at higher levels.

- Challenge: This requires 500 unique reports with over 15,000 graphs (and some rudimentary word clouds for free text).

- Limitations: Need to get these to people in about a week and a half.  Also, my Ctrl+Enter has a limited lifespan.



##R Markdown Solution

- Using the ```render()``` function, you can compile an R Markdown report from within the console or another R Script. Same as if you were to knit from within the Markdown document.

- The ```params``` argument defines the parameters used to override the declared variables in the rendered Markdown file YAML.

- Putting this command inside a ```for``` loop (or custom function with ```apply()```) allows for multiple iterations

```{r, eval=FALSE}

for (i in 1:10) {
  ### <b>
  rmarkdown::render("AORS Demo Report.Rmd",params=list(uic=uiclist$UIC[i]))
  ### </b>
  file.rename(from="AORS_Demo_Report.pdf", to =paste(uiclist$UIC[i],"Graph.pdf"))
  file.copy(from=paste0(getwd(),"/",uiclist$UIC[i]," Graph.pdf"), 
            to = paste0(getwd(),"/UIC Reports/",uiclist$UIC[i]," Graph.pdf"))
  file.remove(paste0(getwd(),"/",uiclist$UIC[i]," Graph.pdf"))
}

```

##Nuances to Consider

- Troubleshooting is challenging.

- Directory changes for files.

- Delete file when re-running or name date/system time.

```{r, eval=FALSE}

for (i in 1:10) {
  rmarkdown::render("AORS Demo Report.Rmd",params=list(uic=uiclist$UIC[i]))
  ### <b>
  file.rename(from="AORS_Demo_Report.pdf", to =paste(uiclist$UIC[i],"Graph.pdf"))
  file.copy(from=paste0(getwd(),"/",uiclist$UIC[i]," Graph.pdf"), 
            to = paste0(getwd(),"/UIC Reports/",uiclist$UIC[i]," Graph.pdf"))
  file.remove(paste0(getwd(),"/",uiclist$UIC[i]," Graph.pdf"))
  ### </b>
}

```


## Final

GitHub Repo for code

MAJ Jim Pleuss
`james.pleuss@westpoint.edu`
845-938-8006



```{r, echo=FALSE, eval=FALSE}
library(tidyverse)
hours=read_csv("aircraft_hours_maintenance_competitors_v2.csv")

#Declare lists of CAB and UICs.
cablist=hours %>% filter(!is.na(CAB) & CAB!="#N/A") %>% distinct(CAB)
uiclist=hours %>% filter(!is.na(CAB) & CAB!="#N/A" & !is.na(UIC)) %>% distinct(UIC) 

###PDF Documents

# for (i in 1:length(uiclist)) {
for (i in 1:10) {
  # i=1
  rmarkdown::render("AORS Demo Report.Rmd",params=list(uic=uiclist$UIC[i]))
  file.rename(from="AORS_Demo_Report.pdf", to =paste(uiclist$UIC[i],"Graph.pdf"))
  file.copy(from=paste0(getwd(),"/",uiclist$UIC[i]," Graph.pdf"), to = paste0(getwd(),"/UIC Reports/",uiclist$UIC[i]," Graph.pdf"))
  file.remove(paste0(getwd(),"/",uiclist$UIC[i]," Graph.pdf"))
}

###HTML Documents

# for (i in 1:length(uiclist)) {
for (i in 1:10) {
  # i=1
  rmarkdown::render("AORS Demo Report.Rmd",params=list(uic=uiclist$UIC[i]))
  file.rename(from="AORS_Demo_Report.html", to =paste(uiclist$UIC[i],"Graph.html"))
  file.copy(from=paste0(getwd(),"/",uiclist$UIC[i]," Graph.html"), to = paste0(getwd(),"/UIC Reports/",uiclist$UIC[i]," Graph.html"))
  file.remove(paste0(getwd(),"/",uiclist$UIC[i]," Graph.html"))
}
```

